A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma

### 2021-03-17 main.tex
new Table 3 and Table 4

%\subsubsection{Table2/legend}

@@

\caption{Univariate/multivariate Cox's proportional hazards regression analyses on OS time of DKK1 gene expression in \acrshort{hnscc}}

@@

@@

\multicolumn{2}{|c!{\color{black}\vrule}}{\multirow{2}{*}{Features}}                                                          & \multicolumn{3}{c|}{Univariate}                                                                                                                                                                                                                & \multicolumn{3}{c|}{Multivariate}                                                                                                                                                                                                               \\ 

@@

\multicolumn{2}{|c!{\color{black}\vrule}}{}                                                                                   & \multicolumn{1}{c!{\color{black}\vrule}}{HR}                                   & \multicolumn{1}{c!{\color{black}\vrule}}{CI95\%}                              & \multicolumn{1}{c!{\color{black}\vrule}}{\textit{P} value}                             & \multicolumn{1}{c!{\color{black}\vrule}}{HR}                                   & \multicolumn{1}{c!{\color{black}\vrule}}{CI95\%}                              & \multicolumn{1}{c!{\color{black}\vrule}}{\textit{P} value}                              \\ 

@@

                                        & Male                                                                                & 1.157                                                                          & 0.843-1.587                                                                   & 0.367                                                                         & 1.178                                                                          & 0.841-1.650                                                                   & 0.342                                                                          \\ 

@@

\multirow{2}{*}{Age at diagnosis}       & {\cellcolor[rgb]{0.62,0.812,0.878}}$<=65y$                                          & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                            \\ 

@@

                                        & $>65y$                                                                              & 1.329                                                                          & 0.990-1.784                                                                   & 0.058                                                                         & 1.462                                                                          & 1.078-1.983                                                                   & \textcolor{red}{0.015}                                                         \\ 

@@

                                        & T3+T4                                                                               & 1.409                                                                          & 1.028-1.931                                                                   & \textcolor{red}{0.033}                                                        & 1.978                                                                          & 1.046-3.737                                                                   & \textcolor{red}{0.036}                                                         \\ 

@@

                                        & N1-3                                                                                & 1.185                                                                          & 0.890-1.577                                                                   & 0.246                                                                         & 1.149                                                                          & 0.805-1.640                                                                   & 0.445                                                                          \\ 

@@

                                        & M1                                                                                  & 4.097                                                                          & 1.009-16.64                                                                   & \textcolor{red}{0.049}                                                        & 6.513                                                                          & 1.415-29.96                                                                   & \textcolor{red}{0.016}                                                         \\ 

@@

                                        & Stage III+IV                                                                        & 1.245                                                                          & 0.882-1.759                                                                   & 0.213                                                                         & 0.597                                                                          & 0.277-1.287                                                                   & 0.188                                                                          \\ 

@@

                                        & Positive                                                                            & 1.591                                                                          & 1.155-2.191                                                                   & \textcolor{red}{0.004}                                                        & 1.601                                                                          & 1.159-2.211                                                                   & \textcolor{red}{0.004}                                                         \\ 

@@

                                        & High                                                                                & 1.364                                                                          & 1.008-1.844                                                                   & \textcolor{red}{0.044}                                                        & 1.302                                                                          & 0.943-1.797                                                                   & 0.109                                                                          \\ 

@@

                                        & High                                                                                & 2.266                                                                          & 1.666-3.082                                                                   & \multicolumn{1}{c|}{\textcolor{red}{***}}                                     & 2.135                                                                          & 1.559-2.924                                                                   & \multicolumn{1}{c|}{\textcolor{red}{***}}                                      \\ 

@@

\multicolumn{8}{|l|}{(\textit{P} value significant codes is denoted: $red<0.05$; *** $<0.001$~~)}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           \\

@@

@@

%\subsubsection{Table4/legend}

@@

\caption{Univariate/multivariate Cox's proportional hazards regression analyses on OS time of ZNF557 gene expression in \acrshort{hnscc}}

@@

@@

\multicolumn{2}{|c!{\color{black}\vrule}}{}                                                                                   & \multicolumn{1}{c!{\color{black}\vrule}}{HR}                                   & \multicolumn{1}{c!{\color{black}\vrule}}{CI95\%}                              & \multicolumn{1}{c!{\color{black}\vrule}}{\textit{P} value}                             & \multicolumn{1}{c!{\color{black}\vrule}}{HR}                                   & \multicolumn{1}{c!{\color{black}\vrule}}{CI95\%}                              & \multicolumn{1}{c!{\color{black}\vrule}}{\textit{P} value}                              \\ 

@@

@@

                                        & Male                                                                                & 1.157                                                                          & 0.843-1.587                                                                   & 0.367                                                                         & 1.163                                                                          & 0.833-1.625                                                                   & 0.375                                                                          \\ 
\multirow{2}{*}{Age at diagnosis}       & {\cellcolor[rgb]{0.62,0.812,0.878}}$<=65y$                                          & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                            \\ 
                                        & $>65y$                                                                              & 1.329                                                                          & 0.990-1.784                                                                   & 0.058                                                                         & 1.328                                                                          & 0.976-1.808                                                                   & 0.071                                                                          \\ 

@@

                                        & T3+T4                                                                               & 1.409                                                                          & 1.028-1.931                                                                   & \textcolor[rgb]{1,0.149,0}{0.033}                                             & 1.961                                                                          & 1.035-3.714                                                                   & \textcolor[rgb]{1,0.149,0}{0.039}                                              \\ 

@@

                                        & N1-3                                                                                & 1.185                                                                          & 0.890-1.577                                                                   & 0.246                                                                         & 1.179                                                                          & 0.824-1.686                                                                   & 0.367                                                                          \\ 

@@

                                        & M1                                                                                  & 4.097                                                                          & 1.009-16.64                                                                   & \textcolor[rgb]{1,0.149,0}{0.049}                                             & 8.478                                                                          & 1.847-38.92                                                                   & \textcolor[rgb]{1,0.149,0}{0.006}                                              \\ 

@@

                                        & Stage III+IV                                                                        & 1.245                                                                          & 0.882-1.759                                                                   & 0.213                                                                         & 0.512                                                                          & 0.239-1.096                                                                   & 0.085                                                                          \\ 

@@

                                        & Positive                                                                            & 1.591                                                                          & 1.155-2.191                                                                   & \textcolor[rgb]{1,0.149,0}{0.004}                                             & 1.631                                                                          & 1.180-2.254                                                                   & \textcolor[rgb]{1,0.149,0}{0.003}                                              \\ 

@@

                                        & High                                                                                & 1.364                                                                          & 1.008-1.844                                                                   & \textcolor[rgb]{1,0.149,0}{0.044}                                             & 1.453                                                                          & 1.055-2.000                                                                   & \textcolor[rgb]{1,0.149,0}{0.022}                                              \\ 

@@

                                        & High                                                                                & 0.465                                                                          & 0.348-0.619                                                                   & \multicolumn{1}{c|}{\textcolor[rgb]{1,0.149,0}{***}}                          & 0.499                                                                          & 0.372-0.669                                                                   & \multicolumn{1}{c|}{\textcolor[rgb]{1,0.149,0}{***}}                           \\ 

@@

>>>>

\subsubsection{Table3/legend} Table 3

@@

\caption{Univariate/multivariate Cox's proportional hazards regression analyses on OS time of CAMK2N1 gene expression in HNSCC}

@@

%\begin{tabularx}{\textwidth}{|p{2.5cm}|l|l|l|l|l|l|l|} 

@@

\multicolumn{2}{|l!{\color{black}\vrule}}{\multirow{2}{*}{Features}}                                                          & \multicolumn{3}{c|}{Univariate}                                                                                                                                                                                                                & \multicolumn{3}{c|}{Multivariate}                                                                                                                                                                                                               \\ 

@@

\multicolumn{2}{|l!{\color{black}\vrule}}{}                                                                                   & \multicolumn{1}{l!{\color{black}\vrule}}{HR}                                   & \multicolumn{1}{c!{\color{black}\vrule}}{CI95\%}                              & \multicolumn{1}{l!{\color{black}\vrule}}{\textit{P}~value}                    & \multicolumn{1}{l!{\color{black}\vrule}}{HR}                                   & \multicolumn{1}{c!{\color{black}\vrule}}{CI95\%}                              & \multicolumn{1}{l!{\color{black}\vrule}}{\textit{P}~value}                     \\ 

@@

                                        & Male                                                                                & 1.157                                                                          & 0.843-1.587                                                                   & 0.367                                                                         & 1.076                                                                          & 0.767-1.510                                                                   & 0.671                                                                          \\ 

@@

\multirow{2}{*}{Age at diagnosis}       & {\cellcolor[rgb]{0.62,0.812,0.878}}=65y                                             & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                            \\ 

@@

                                        & 65y                                                                                 & 1.329                                                                          & 0.990-1.784                                                                   & 0.058                                                                         & 1.391                                                                          & 1.025-1.888                                                                   & \textcolor{red}{0.034}                                                         \\ 

@@

                                        & T3+T4                                                                               & 1.409                                                                          & 1.028-1.931                                                                   & \textcolor{red}{0.033}                                                        & 1.982                                                                          & 1.048-3.745                                                                   & \textcolor{red}{0.035}                                                         \\ 

@@

                                        & N1-3                                                                                & 1.185                                                                          & 0.890-1.577                                                                   & 0.246                                                                         & 1.145                                                                          & 0.801-1.636                                                                   & 0.457                                                                          \\ 

@@

                                        & M1                                                                                  & 4.097                                                                          & 1.009-16.644                                                                  & \textcolor{red}{0.049}                                                        & 7.314                                                                          & 1.590-33.631                                                                  & \textcolor{red}{0.011}                                                         \\ 

@@

                                        & Stage III+IV                                                                        & 1.245                                                                          & 0.882-1.759                                                                   & 0.213                                                                         & 0.621                                                                          & 0.287-1.343                                                                   & 0.226                                                                          \\ 

@@

                                        & Positive                                                                            & 1.591                                                                          & 1.155–2.191                                                                   & \textcolor{red}{0.004}                                                        & 1.631                                                                          & 1.182-2.250                                                                   & \textcolor{red}{0.003}                                                         \\ 

@@

                                        & High                                                                                & 1.364                                                                          & 1.008-1.844                                                                   & \textcolor{red}{0.044}                                                        & 1.363                                                                          & 0.990-1.875                                                                   & 0.058                                                                          \\ 

@@

                                        & High                                                                                & 2.101                                                                          & 1.572-2.809                                                                   & \multicolumn{1}{c|}{\textcolor{red}{***}}                                     & 2.007                                                                          & 1.490-2.704                                                                   & \multicolumn{1}{c|}{\textcolor{red}{***}}                                      \\ 

@@

\multicolumn{8}{|l|}{(\textit{P}~value significant codes is denoted: red \textless{} 0.05; *** \textless{} 0.001)}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                               \\

@@

} % end of \resizebox

@@

\subsubsection{Table4/legend} Table 4

@@

\caption{Univariate/multivariate Cox's proportional hazards regression analyses on OS time of IL19 gene expression in HNSCC}

@@

\begin{tabular}{|l|l|l|l|l|l!{\color{black}\vrule}l!{\color{black}\vrule}l!{\color{black}\vrule}} 

@@

\multicolumn{2}{|l!{\color{black}\vrule}}{}                                                                                   & \multicolumn{1}{l!{\color{black}\vrule}}{HR}                                   & \multicolumn{1}{c!{\color{black}\vrule}}{CI95\%}                              & \multicolumn{1}{l!{\color{black}\vrule}}{\textit{P}~value}                    & HR                                   & \multicolumn{1}{c!{\color{black}\vrule}}{CI95\%} & \textit{P}~value                           \\ 

@@

\multirow{2}{*}{Gender}                 & \multicolumn{1}{l!{\color{black}\vrule}}{{\cellcolor[rgb]{0.62,0.812,0.878}}Female} & \multicolumn{1}{l!{\color{black}\vrule}}{{\cellcolor[rgb]{0.62,0.812,0.878}}1} & \multicolumn{1}{l!{\color{black}\vrule}}{{\cellcolor[rgb]{0.62,0.812,0.878}}} & \multicolumn{1}{l!{\color{black}\vrule}}{{\cellcolor[rgb]{0.62,0.812,0.878}}} & {\cellcolor[rgb]{0.62,0.812,0.878}}1 & {\cellcolor[rgb]{0.62,0.812,0.878}}              & {\cellcolor[rgb]{0.62,0.812,0.878}}        \\ 

@@

                                        & Male                                                                                & 1.157                                                                          & 0.843-1.587                                                                   & 0.367                                                                         & 1.183                                & 0.847-1.652                                      & 0.325                                      \\ 
\hhline{>{\arrayrulecolor[rgb]{0.255,0.255,0.255}}|----->{\arrayrulecolor{black}}->{\arrayrulecolor{black}}->{\arrayrulecolor{black}}-|}
\multirow{2}{*}{Age at diagnosis}       & {\cellcolor[rgb]{0.62,0.812,0.878}}=65y                                             & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1 & {\cellcolor[rgb]{0.62,0.812,0.878}}              & {\cellcolor[rgb]{0.62,0.812,0.878}}        \\ 
\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{2-5}\arrayrulecolor{black}\cline{6-6}\arrayrulecolor{black}\cline{7-7}\arrayrulecolor{black}\cline{8-8}
                                        & 65y                                                                                 & 1.329                                                                          & 0.990-1.784                                                                   & 0.058                                                                         & 1.481                                & 1.087-2.018                                      & \textcolor{red}{0.013}                     \\ 
\hhline{>{\arrayrulecolor[rgb]{0.255,0.255,0.255}}|----->{\arrayrulecolor{black}}->{\arrayrulecolor{black}}->{\arrayrulecolor{black}}-|}

@@

\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{2-5}\arrayrulecolor{black}\cline{6-6}\arrayrulecolor{black}\cline{7-7}\arrayrulecolor{black}\cline{8-8}
                                        & T3+T4                                                                               & 1.409                                                                          & 1.028-1.931                                                                   & \textcolor{red}{0.033}                                                        & 2.175                                & 1.152-4.106                                      & \textcolor{red}{0.017}                     \\ 
\hhline{>{\arrayrulecolor[rgb]{0.255,0.255,0.255}}|----->{\arrayrulecolor{black}}->{\arrayrulecolor{black}}->{\arrayrulecolor{black}}-|}

@@

\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{2-5}\arrayrulecolor{black}\cline{6-6}\arrayrulecolor{black}\cline{7-7}\arrayrulecolor{black}\cline{8-8}
                                        & N1-3                                                                                & 1.185                                                                          & 0.890-1.577                                                                   & 0.246                                                                         & 1.237                                & 0.864-1.770                                      & 0.245                                      \\ 
\hhline{>{\arrayrulecolor[rgb]{0.255,0.255,0.255}}|----->{\arrayrulecolor{black}}->{\arrayrulecolor{black}}->{\arrayrulecolor{black}}-|}

@@

\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{2-5}\arrayrulecolor{black}\cline{6-6}\arrayrulecolor{black}\cline{7-7}\arrayrulecolor{black}\cline{8-8}
                                        & M1                                                                                  & 4.097                                                                          & 1.009-16.644                                                                  & \textcolor{red}{0.049}                                                        & 8.629                                & 1.879-39.63                                      & \textcolor{red}{0.006}                     \\ 
\hhline{>{\arrayrulecolor[rgb]{0.255,0.255,0.255}}|----->{\arrayrulecolor{black}}->{\arrayrulecolor{black}}->{\arrayrulecolor{black}}-|}

@@

\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{2-5}\arrayrulecolor{black}\cline{6-6}\arrayrulecolor{black}\cline{7-7}\arrayrulecolor{black}\cline{8-8}
                                        & Stage III+IV                                                                        & 1.245                                                                          & 0.882-1.759                                                                   & 0.213                                                                         & 0.476                                & 0.222-1.024                                      & 0.057                                      \\ 
\hhline{>{\arrayrulecolor[rgb]{0.255,0.255,0.255}}|----->{\arrayrulecolor{black}}->{\arrayrulecolor{black}}->{\arrayrulecolor{black}}-|}

@@

\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{2-5}\arrayrulecolor{black}\cline{6-6}\arrayrulecolor{black}\cline{7-7}\arrayrulecolor{black}\cline{8-8}
                                        & Positive                                                                            & 1.591                                                                          & 1.155–2.191                                                                   & \textcolor{red}{0.004}                                                        & 1.63                                 & 1.180-2.252                                      & \textcolor{red}{0.003}                     \\ 
\hhline{>{\arrayrulecolor[rgb]{0.255,0.255,0.255}}|----->{\arrayrulecolor{black}}->{\arrayrulecolor{black}}->{\arrayrulecolor{black}}-|}

@@

\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{2-5}\arrayrulecolor{black}\cline{6-6}\arrayrulecolor{black}\cline{7-7}\arrayrulecolor{black}\cline{8-8}
                                        & High                                                                                & 1.364                                                                          & 1.008-1.844                                                                   & \textcolor{red}{0.044}                                                        & 1.62                                 & 1.173-2.238                                      & \textcolor{red}{0.003}                     \\ 
\hhline{>{\arrayrulecolor[rgb]{0.255,0.255,0.255}}|----->{\arrayrulecolor{black}}->{\arrayrulecolor{black}}->{\arrayrulecolor{black}}-|}

@@

\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{2-5}\arrayrulecolor{black}\cline{6-6}\arrayrulecolor{black}\cline{7-7}\arrayrulecolor{black}\cline{8-8}
                                        & High                                                                                & 0.472                                                                          & 0.351-0.635                                                                   & \multicolumn{1}{c|}{\textcolor{red}{***}}                                     & \multicolumn{1}{l|}{0.459}           & 0.340-0.619                                      & \multicolumn{1}{c|}{\textcolor{red}{***}}  \\ 
\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{1-6}\arrayrulecolor{black}\cline{7-7}\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{8-8}

@@

}% end of \resizebox
